A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-06-26 paper/main.tex
sentence regarding continuous regressors

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word.
% phonemes
The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and each event
modeled as boxcar function from onset to offset of the corresponding
phoneme.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech.
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the
average length of phonemes.
% low-level nuisance regressors
Lastly, we used continuous information about auditory features (left-right
difference in volume and root mean squared volume) that was averaged across the
length of every movie frame (\unit[40]{ms}) to capture variance correlating with
low-level perceptual processes.
% convolving
Time series of events were convolved with FSL's ``Double-Gamma HRF'' as a model
of the hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix to compensate for
regional differences between modeled and actual HRF.
% motion parameters & temporal filtering of design
% motion parameter are filtered, too. See FSL manual:
% ``All (confound) EVs will be filtered to match the processing applied to the
% input data''
Finally, six motion parameters were used as additional nuisance regressors and
the design was subjected to the same temporal filtering as the BOLD time
series.

>>>>

% intro to analysis
We implemented a standard three-level, voxel-wise general linear model (GLM) to
average parameter estimates across the eight stimulus segments, and later across
19 subjects.
% 1st lvl
At the first level analyzing each segment for each subject individually, we
created 26 regressors based on events drawn from the annotation (see Table
\ref{tab:regressors}).
% part-of-speech labels: labels to events, top 20
The 20 most often occurring detailed part-of-speech labels (\texttt{nn} with
N=\rNnAll\space to text{prf} with N=\rPrfAll) were modeled as boxcar function
from onset to offset of each word.
% path-of-speech labels: remaining labels
The remaining other part-of-speech labels were pooled to a single new label
(\texttt{tag\_other}; N=\rTagotherAll) and each event was modeled as a boxcar
function from onset to offset of the corresponding word.
% phonemes
The 80 most often occurring phonemes (\texttt{n} with N=6053 to \texttt{IY1}
with N=32) were pooled to \texttt{phonemes} (N=\rPhonesAll) and each event
modeled as boxcar function from onset to offset of the corresponding phoneme.
% sentence (endings)
The end of each complete grammatical sentence was modeled as an impulse event
(N=\rSentenceAll) to capture variance correlating with sentence comprehension.
% no-speech intro
``No-speech'' events (\texttt{no-sp}; N=\rNospAll) serving as a control
condition were created by the following rationale: events were fitted into
longer lasting intervals between onsets and offsets of words and thus within
intervals without audible speech.
% minimum distance to words
Each event of the no-speech condition had to have a minimum distance of
\unit[1.8]{s} to an onsets or offsets of a word, and to each onset to another
event of the no-speech condition.
% length of no-speech events
A length of \unit[70]{ms} was chosen for no-speech events matching the average
length of phonemes.
% low-level nuisance regressors
Lastly, we used continuous bins of information about auditory features
(left-right difference in volume and root mean square energy) that was averaged
across the length of every movie frame (\unit[40]{ms}) to capture variance
correlating with low-level perceptual processes.
% convolving
Time series of events were convolved with FSL's ``Double-Gamma HRF'' as a model
of the hemodynamic response function to create the actual regressors.
% reference to figure ``correlation of regressors''
The Pearson correlation coefficients of the 26 regressors across the time course
of all stimulus segments can be seen in Figure \ref{fig:reg-corr}.
% temporal derivatives
Temporal derivatives were also included in the design matrix to compensate for
regional differences between modeled and actual HRF.
% motion parameters & temporal filtering of design motion parameter are
% filtered, too. See FSL manual: ``All (confound) EVs will be filtered to match
% the processing applied to the input data''
Finally, six motion parameters were used as additional nuisance regressors and
the design was subjected to the same temporal filtering as the BOLD time series.
